# Listen to the problem

It's useful to get an understanding of what your resources are like when *viewed* with a screen reader. It's very straight forward to get a simple screen reader going on google chrome, you can then try out your resources. Emma Cliffe has made this useful resource to get going: [Getting started with with a simple screen reader.](https://people.bath.ac.uk/cspehj/coventry/arclengthInR.html)

## Desmos audio trace

When you are in the equation window on the side of the Desmos graphing calculator pres `alt` and `t` to get screen reader menu. You can then click 'hear graph' to get an audio representation of the graph. The [accessibility notes for Desmos](https://www.desmos.com/accessibility) will tell you more about this feature. 

Can you identify which graph is being played via the Desmos audio trace?

### Challenge 1

```{r, echo=FALSE}
knitr::include_url("https://www.desmos.com/calculator/ynybna6ahr?embed")
```

```{r, echo=FALSE}
knitr::include_url("https://www.desmos.com/calculator/q83pv7enih?embed")
```

### Challenge 2

```{r, echo=FALSE}
knitr::include_url("https://www.desmos.com/calculator/tpbus3mq8g?embed")
```

```{r, echo=FALSE}
knitr::include_url("https://www.desmos.com/calculator/inxf0yqfu5?embed")
```
